Easy as Pi, Volume II: On the Goodput and Energy of Network Coding Schemes in the Raspberry Pi

### 2016-08-16 introduction.tex
Advances in the introduction description

A benefit of using the \ac{Raspi} as development platform is its large
community of supporters. By running standard operating systems such as
Linux or Windows, this permits to utilize standard, well tested and
reliable tools to administrate and maintain these networks in
a flexible, stable and supported manner which is a major requirement
to make a scalable deployment. Moreover, by enabling system designers to
configure and deploy several devices at the same time, possible deployments
of tens, hundreds or even thousands of Raspberry Pi's would allow to
analyze representative data patterns of the \ac{IoT}. Different use cases of
\ac{IoT} applications employing the \ac{Raspi} as a building block can be found
in the literature. A basic study of the \ac{Raspi} as a possible device
for sensor applications can be found in \cite{vujovic2014raspberry}.
Authors in \cite{kruger2015rapid} consider using the \ac{Raspi} as an
\ac{6LoWPAN} gateway for a set of sensor and mobile devices to an
\ac{IP} version 6 network. In \cite{mahmoud2016sensorian}, a general
purpose sensoring platform for \ac{IoT} is presented using the \ac{Raspi}
as its basic building block.

>>>>

A benefit of using the \ac{Raspi} as development platform is its large
community of supporters. By running standard operating systems such as
Linux or Windows, this permits to utilize standard, well tested and
reliable tools to administrate and maintain these networks in
a flexible, stable and supported manner which is a major requirement
to make a scalable deployment. Moreover, by enabling system designers to
configure and deploy several devices at the same time, possible deployments
of tens, hundreds or even thousands of Raspberry Pi's would allow to
analyze representative data patterns of the \ac{IoT}. Different use cases of
\ac{IoT} applications employing the \ac{Raspi} as a building block can be found
in the literature. A basic study of the \ac{Raspi} as a possible device
for sensor applications can be found in \cite{vujovic2014raspberry}.
Authors in \cite{kruger2015rapid} consider using the \ac{Raspi} as an
\ac{6LoWPAN} gateway for a set of sensor and mobile devices to an
\ac{IP} version 6 network. In \cite{mahmoud2016sensorian}, a general
purpose sensoring platform for \ac{IoT} is presented using the \ac{Raspi}
as its basic building block. Other interesting \ac{IoT} use cases
are the works presented in \cite{wirz2015enabling,alletto2016indoor}. In the first
of these works, many \ac{Raspi}s are used as controllable smart devices
with network connectivity that may ubiquously interact with different users,
each represented by a mobile device through a smartphone application.
The second work considers \ac{Raspi}s as a data processing unit
for disseminating artwork content in smart museums.
